A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by a pile of money from a funding agency.}

### 2017-02-16 paper/paper.tex
Variety is the spice of life

Our results so far suggest that \McSplit\ has broadly similar performance
trends to the constraint programming, forward-checking (CP-FC) algorithm of
\citet{DBLP:conf/cp/NdiayeS11}, but with much lower constant factors. Indeed,
in \cref{figure:33ved-james-versus-cp-fc-nodes-scatter} we plot the number of
recursive calls made by our algorithm on the $y$-axis versus the number made by
CP-FC on the $x$-axis, for the labelled, unconnected problem instances. (Rather
than a simple scatter plot, we use darker colours to indicate a higher density
of points around a location.) We see a close correlation: we typically do
slightly less work, and sometimes do more, but instances with more than one
order of magnitude difference in search space size are rare.

@@

\begin{figure}[t]
    \centering
    \includegraphics*{gen-graph-33ved-james-versus-cp-fc-nodes-scatter.pdf}
    \caption{Size of the search space for \McSplit\ versus CP-FC on the
    labelled, directed, unconnected instances which were solved within the
    timeout by both algorithms.}
    \label{figure:33ved-james-versus-cp-fc-nodes-scatter}
\end{figure}

@@

What about our relationship to the $k\downarrow$ of \citet{UpcomingAAAIPaper}?
\Cref{figure:sip-james-versus-kdown-nodes-scatter} plots the number of
recursive calls made by $k\downarrow$ and \McSplit\ on each of the subgraph
isomorphism instances. Although \McSplit\ is the faster algorithm overall, it
explores more search nodes than $k\downarrow$ for most instances.

@@

\begin{figure}[h]
    \centering
    \includegraphics*{gen-graph-sip-james-versus-kdown-nodes-scatter.pdf}
    \caption{Size of the search space for \McSplit$\downarrow$\ versus $k\downarrow$ on the
    large subgraph isomorphism instances which were solved within the
    timeout by both algorithms.}\label{figure:sip-james-versus-kdown-nodes-scatter}
\end{figure}

>>>>

Our results so far suggest that \McSplit\ has broadly similar performance
trends to the constraint programming, forward-checking (CP-FC) algorithm of
\citet{DBLP:conf/cp/NdiayeS11}, but with much lower constant factors. Indeed,
in \cref{figure:prettyheatmaps1,figure:prettyheatmaps2} we plot the number of
recursive calls made by our algorithm on the $y$-axis versus the number made by
CP-FC on the $x$-axis, for the labelled, unconnected problem instances. (Rather
than a simple scatter plot, we use darker colours to indicate a higher density
of points around a location.) We see a close correlation: we typically do
slightly less work, and sometimes do more, but instances with more than one
order of magnitude difference in search space size are rare.

@@

\begin{figure*}[t]
    \centering\subfiguretopcaptrue
    \subfigure[][Unlabelled, undirected instances] {\label{figure:prettyheatmaps1}
    \includegraphics*{gen-graph-plain-james-versus-cp-fc-nodes-scatter.pdf}
    }\subfigure[][Labelled, directed instances] {\label{figure:prettyheatmaps2}
    \includegraphics*{gen-graph-33ved-james-versus-cp-fc-nodes-scatter.pdf}
    }\subfigure[][Subgraph isomorphism instances]{\label{figure:prettyheatmaps3}
    \includegraphics*{gen-graph-sip-james-versus-kdown-nodes-scatter.pdf}
}
    \caption{Relative search space sizes for instances which were solved by both algorithms within the timeout.}
    \label{figure:prettyheatmaps}
\end{figure*}

@@

What about our relationship to the $k\downarrow$ of \citet{UpcomingAAAIPaper}?
\Cref{figure:prettyheatmaps3} plots the number of
recursive calls made by $k\downarrow$ and \McSplit\ on each of the subgraph
isomorphism instances. Although \McSplit\ is the faster algorithm overall, it
explores more search nodes than $k\downarrow$ for most instances.

@@
